---
title: "Homework 1"
author: "Mingee Choi"
date: 09/24/2022
output: github_document
---


# Problem 1

To find basic description of dataset:
```{r}
data("penguins", package = "palmerpenguins")
summary(penguins)
```
To find size of the dataset (nrow and ncol):
```{r}
x=data.frame(penguins)
y=data.frame(penguins)
nrow(x)
ncol(y)
```

**Description of dataset:**
*variable names: species, island, bill_length_mm, bill_depth_mm, flipper_length_mm, body_mass_g, sex, and year
*Values of important variables: 
  *Sex: female=165, male=168
  *Species: Adelie=152, Chinstrap=68, Gentoo=124
  *Island: Biscoe=168, Dream=124, Torgersen=52
  *Means: Bill Length (mm)=43.92, Bill Depth (mm)=17.15, Body Mass (g)=4202
  *Median: Bill Length (mm)=44.45, Bill Depth (mm)=17.30, Body Mass (g)=4050
*Rows=334 and Columns=8
*Mean flipper length:200.9

####Scatterplot of flipper length vs bill length
To make scatterplot with species in different colors:
```{r plot_problem2, message=FALSE}
library(tidyverse)
ggplot(penguins, aes(x=flipper_length_mm, y=bill_length_mm))+geom_point(aes(color=species))
ggsave("scatter_plot.pdf")
```

# Problem 2
Creating a dataframe
```{r}
problem2_df = tibble(
  a=rnorm(n=10),
  result <- a>0,
  vec_char = c("Here", "Is", "A", "Character", "Vector", "For", "Homework", "1", "Problem", "2"),
  vec_factor = factor(c(1,2,3,1,2,3,1,2,3,1)),
)
  problem2_df
  
```