---
title: "Homework 1"
author: "Mingee Choi"
date: 09/24/2022
output: github_document
---


# Problem 1

To find basic description of dataset:
```{r}
data("penguins", package = "palmerpenguins")
summary(penguins)
```
To find size of the dataset (nrow and ncol):
```{r}
x=data.frame(penguins)
y=data.frame(penguins)
nrow(x)
ncol(y)
```

**Description of dataset:**
* variable names: species, island, bill_length_mm, bill_depth_mm, flipper_length_mm, body_mass_g, sex, and year

* Values of important variables: 
  *Sex: female=165, male=168
  
  *Species: Adelie=152, Chinstrap=68, Gentoo=124
  
  *Island: Biscoe=168, Dream=124, Torgersen=52
  
  *Means: Bill Length (mm)=43.92, Bill Depth (mm)=17.15, Body Mass (g)=4202
  
  *Median: Bill Length (mm)=44.45, Bill Depth (mm)=17.30, Body Mass (g)=4050
  
*Rows=334 and Columns=8

*Mean flipper length:200.9

**Scatterplot of flipper length vs bill length**
To make scatterplot with species in different colors:
```{r plot_problem2, warning=FALSE, message=FALSE}
library(tidyverse)
ggplot(penguins, aes(x=flipper_length_mm, y=bill_length_mm))+geom_point(aes(color=species))
ggsave("scatter_plot.pdf")
```

# Problem 2
Creating a dataframe
```{r}
problem2_df = tibble(
  norm_samp = rnorm(n=10),
  vec_logical <- norm_samp>0,
  vec_char = c("1", "2", "3", "4", "5", "6", "7", "8", "9", "10"),
  vec_factor = factor(c(1,2,3,1,2,3,1,2,3,1)),
)
  problem2_df
  
#Taking the mean of each variable in my dataframe:
mean(problem2_df$norm_samp)
mean(problem2_df$vec_char)
mean(problem2_df$vec_logical)
mean(problem2_df$vec_factor)
```
Finding the mean of a random sample of size 10 from a standard normal distribution (a) works, but finding the mean of the logical vector, character vector, and factor vector doesn't work.

```{r, results='hide', warning=FALSE, message=FALSE}
as.numeric(problem2_df$vec_char)
as.numeric(problem2_df$vec_logical)
as.numeric(problem2_df$vec_factor)
```
Numerical values are assigned to the different vectors. The logical vector takes a value of 1 ("True") or 0 ("False"). The character vector takes on values from 1-10, and the factor vector takes on values I assigned. Since I can only take the mean of numerical values, this explains why I couldn't take the mean of the logical, character, and factor values before I converted them into numerical values. 


